Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-05 paper/paper.tex
+ applying the synthesiser on the running example

Next, the following Jury matrix
$M = [m_{ij}]_{(2N−2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right)
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \texttt{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\texttt{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
\end{array}
\right.
$$
%
where $k \in \mathbb{Z}$, such that $0 < k < N − 2$. 
$S(z)$ is the
characteristic polynomial of a stable system if and only if
the following four propositions hold:
\begin{itemize}
\item $R_1: S(1) > 0$;
\item $R_2: (−1)^N S(−1) > 0$;
\item $R_3: |a_0| < a_N$;
\item $R_4: m_{11} > 0 \wedge m_{31}>0 \wedge m_{51}>0 \wedge \cdots \wedge m_{(2N{-}3)(1)}>0$.
\end{itemize}

@@

\paragraph{Running example synthesis}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
\cdsay{Pascal, I also need the candidate solutions here}
% Counterexample from first cruisecontrol02.c benchmark with uncertainty and
% nondeterminism:
% 1) { (0.02634525299072265625, 0.9979267120361328125, -0.99768829345703125) }

>>>>

Next, the following Jury matrix
$M = [m_{ij}]_{(2N−2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right)
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \texttt{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\texttt{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
\end{array}
\right.
$$
%
where $k \in \mathbb{Z}$, such that $0 < k < N - 2$. 
$S(z)$ is the
characteristic polynomial of a stable system if and only if
the following four propositions hold:
\begin{itemize}
\item $R_1: S(1) > 0$;
\item $R_2: (−1)^N S(−1) > 0$;
\item $R_3: |a_0| < a_N$;
\item $R_4: m_{11} > 0 \wedge m_{31}>0 \wedge m_{51}>0 \wedge \cdots \wedge m_{(2N{-}3)(1)}>0$.
\end{itemize}

@@

\paragraph{Using the program synthesiser for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with a candidate solution that has all coefficients 0.
In the first {\sc verify} phase we obtain the following counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.02634525299072265625\\
\Delta D_G(z) = 0.9979267120361328125z-0.99768829345703125
\end{array}
$$

We add this counterexample to {\sc inputs} and initiate the {\sc
  synthesise} phase, where we get the following candidate solution:

$$
\begin{array}{ll}
N_C(z) {=} 4.00888156890869140625z^2{-}0.00041961669921875z\\
\qquad\qquad -0.000213623046875\\
D_C(z) {=} -0.003753662109375z^2{+}7.37355804443359375z \\
\qquad\qquad -7.2847900390625\\
\end{array}
$$

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and we get a new counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.02644824981689453125\\
\Delta D_G(z) {=} 1.00053310394287109375z{-}1.0014629364013671875
\end{array}
$$

After adding this new counterexample to the set of {\sc inputs}, in the 
next {\sc synthesise} phase, we get a new candidate solution that holds
for both uncertainties in {\sc Inputs}:

$$
\begin{array}{ll}
N_C(z) {=} 7.515781402587890625z^2{-}4.385616302490234375z\\
\qquad\qquad +4.142093658447265625\\
D_C(z) {=} -3.52398681640625z^2{-}1.530254364013671875z \\
\qquad\qquad +7.58094024658203125\\
\end{array}
$$

This candidate solution is validated as the final solution by the next 
{\sc verify} phase, which fails to find a new counterexample (i.e. returns UNSAT).

% Counterexample from first cruisecontrol02.c benchmark with uncertainty and
% nondeterminism:
% 1) { (0.02634525299072265625, 0.9979267120361328125, -0.99768829345703125) }
